---
title: MetaCheck Report
subtitle: "%s"
author: "%s"
metacheck:
  version: "%s"
  report-created: "%s"
format:
  html:
    theme: 
      light: flatly
      dark: darkly
    respect-user-color-scheme: true
    toc: true
    toc-title: >
      <ul class="emoji-key">
        <li class="red">⚠️ possible problems detected;</li> 
        <li class="yellow">🔍 something to check;</li> 
        <li class="green">✅️ no problems detected;</li>  
        <li class="info">ℹ️ informational only;</li>  
        <li class="na">⚪️ not applicable;</li>  
        <li class="fail">☠️ check failed</li>
      <ul>
      <hr/>
      **Table of Contents**
    toc-location: right
    toc-expand: 3
    page-layout: full
    title-block-banner: "#15342A"    #"#327118"
    title-block-banner-color: "white"
    link-external-newwindow: true
    embed-resources: true
    format-links: false
    smooth-scroll: true
execute: 
  echo: false
  error: true
---

<style>
  #TOC * { border-left: none; }
  #TOC > ul { border-left: 1px solid #15342A; }
  #TOC > ul > li > ul > li { text-indent: -1.2em; margin-left: 1.2em; }
  main h2, main h3 { margin-left: -20px; }
  main h2 { font-size: 150%; font-face: italics; }
  main h3 { font-size: 125%; }
  main h4 { font-size: 110%; }
  .emoji-key li { margin-bottom: 0.5em; }
  section::before { content: '' !important; }
  th { background-color: #555; color: white; }
  table.dataTable, .dataTables_scrollBody { margin: 0.5em 0; }
  #info { position: absolute; top: 2.5em; right: 2.5em; color: white; }
  #info a { color: white !important; }
  .quarto-dark tr.even { background-color: #333; }
  .quarto-dark tr.odd { background-color: #222; }
  .quarto-dark div.datatables { color: white; }
  .quarto-dark table.dataTable { border: 1px solid #555; }
  table strong { color: red; }
  .quarto-dark table strong { color: yellow; }
  summary { color: #333; }
  .quarto-dark summary { color: #CCC; }
</style>

::: {#info}
[MetaCheck](http://www.scienceverse.org/metacheck) version {{< meta metacheck.version >}}  
Report Created: {{< meta metacheck.report-created >}}  
%s <!-- doi, if exists -->
:::

[Metacheck](https://www.scienceverse.org/metacheck/) is a tool that screens scientific manuscripts and aims to identify potential issues for improvement, thereby guiding researchers towards best practices. Metacheck is developed to help researchers correctly and completely report statistical results, automatically retrieve possible relevant information about citations, and improve how researchers share data, code, and preregistrations.

::: {.callout-tip title="Learn More" collapse="true"}

Metacheck combines existing and new checks in a module-based tool. It mainly relies on text search, retrieving information from external sources through API’s or web-scraping, but it also incorporates tool that use machine learning classifiers or large language models. The use of LLM’s is always optional. The development of Metacheck is guided by our [values statement](https://docs.google.com/document/d/1bbIkgUaiz3fpTXAeTF3h-gsfhqWEBN_n6OBcbFLfXjw/edit?tab=t.0). 

Metacheck often needs to balance false positives against false negatives, and prioritizes preventing false negatives. Like a spelling checker, which often highlights words that are not spelled incorrectly, Metacheck modules will contain false positives. We hope their rate is acceptable, given opportunities for improvement that Metacheck identifies. Modules are currently primarily validated on the psychological literature.

Metacheck is under continuous development. Issues can be submitted [on Github](https://github.com/scienceverse/metacheck/issues), and suggestions for improvement or feedback can be sent to D.Lakens@tue.nl.

:::

<!-- Demo -->

Everything below here is for test purposes and removed when using this template to create a report.

```{r}
#| include: false
library(metacheck)
```

## Summary

- ✅️ [No problems detected](#module-1){.green} Detected evidence of good practice or no evidence of poor practice.
- 🔍 [Something to check](#module-2){.yellow}: Detected something you should check.
- ⚠️ [Possible problems detected](#module-3){.red}: A possible poor practice detected.
- ℹ️ [Informational only](#module-4){.info}: Info that isn't necessarily good/questionable/poor practice.
- ⚪️ [Not applicable](#module-5){.na}: This check isn't relevant to this paper.
- ☠️ [Check failed](#module-6){.fail}: This is usually when something goes wroing and there is an uncaught error in the module.

## General Modules

### ✅ Module 1 {.green}

<details>
  <summary>View feedback</summary>
  <div>
Adipiscing massa leo neque cubilia, volutpat, curae aptent scelerisque, eget quam placerat. Vitae inceptos himenaeos gravida semper viverra platea. Lacus ac congue facilisis urna pharetra ornare fermentum commodo, senectus fames dictumst magna tempor.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(id = 1:3, text = c("Dolor urna mus libero dui consequat quisque sapien nibh curae eros.", 
"Consectetur hac integer urna pharetra ridiculus penatibus magna magnis nisi ac?", 
"Adipiscing ultrices imperdiet lectus bibendum massa facilisis suscipit."
)), class = "data.frame", row.names = c(NA, -3L))

# display table -----------------------------------
metacheck::report_table(table, c(.1, .9), 3, FALSE)
```

```{r}
#| results: 'asis'

marg_ref <- bibentry(
  bibtype = "Article",
  title = "The Prevalence of Marginally Significant Results in Psychology Over Time",
  author = "Olsson-Collentine, A., van Assen, M. A. L. M., & Hartgerink, C. H. J.",
  year = "2019",
  journal = "Psychological Science",
  volume = 30,
  issue = 4,
  pages = "576--586",
  doi = "10.1177/0956797619830326"
)

format_ref(marg_ref) |> cat()
```

`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

### 🔍 Module 2 {#module-2 .yellow}

<details>
  <summary>View feedback</summary>
  <div>

Elit potenti aliquet, pulvinar est nascetur felis cubilia vel scelerisque dapibus mus conubia. Ut laoreet taciti morbi cum.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(c(
  "Amet accumsan inceptos aliquam cras non commodo sapien vulputate diam odio fermentum magnis ornare tristique.", 
  "Lorem habitant sem enim libero nostra lacus pharetra aptent rutrum vehicula.",
  "Ipsum taciti non pharetra morbi bibendum sociis congue risus pellentesque elementum!", 
  "Elit fringilla penatibus proin diam erat torquent iaculis vestibulum platea dictumst ligula.", 
  "Amet conubia ultricies arcu consequat mattis auctor metus."
)), names = "", class = "data.frame", row.names = c(NA, -2L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

### ⚠️ Module 3 {#module-3 .red}

<details>
  <summary>View feedback</summary>
  <div>
  
Ipsum in magnis proin ligula nisi parturient, morbi sagittis dis tellus. Pretium ante mauris nulla ac, fusce sollicitudin feugiat semper fermentum massa? Ullamcorper a tellus, pulvinar augue montes molestie proin quis molestie tortor. Habitant conubia cursus conubia, odio duis, pharetra, ad magnis pretium. Sem montes nullam vitae faucibus nunc pulvinar ultrices dignissim risus imperdiet eros fames viverra semper.

Elit porta mattis, inceptos euismod massa enim aenean ullamcorper netus odio nunc. Molestie arcu montes at nisl eget sed.

Ipsum viverra quam nunc ullamcorper congue aptent molestie vivamus per quam cursus parturient? Quam montes euismod pellentesque magnis torquent magna, iaculis mollis suspendisse? Semper ut primis auctor a tempus duis libero sociosqu fringilla. Phasellus neque vitae fusce tincidunt velit sapien – sodales eleifend orci nisl. Blandit platea nullam quisque, donec tempor curabitur posuere cursus? Platea vivamus malesuada, risus habitant ultrices conubia semper dui proin nibh.

```{r}
#| echo: false
# table data ------------------------------------
table <- structure(list(id = 1:5, text = c("Lorem semper tempus libero habitant faucibus cursus venenatis natoque volutpat est ultricies penatibus nisl lacinia.", 
"Lorem cras bibendum facilisi porta sagittis a convallis fames erat dui netus cubilia.", 
"Adipiscing auctor litora scelerisque tincidunt ullamcorper volutpat mattis ultrices lectus rutrum.", 
"Elit nisi cras pharetra etiam semper sollicitudin interdum magnis facilisi.", 
"Ipsum per platea varius vel condimentum posuere gravida cum laoreet commodo."
)), class = "data.frame", row.names = c(NA, -5L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

## Introduction Modules

### ℹ️ Module 4 {#module-4 .info}

<details>
  <summary>View feedback</summary>
  <div>
    
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

## Methods Modules

### ⚪️ Module 5 {#module-5 .na}

<details>
  <summary>View feedback</summary>
  <div>
    
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

## Results Modules

### ☠️ Module 6 {#module-6 .fail}

<details>
  <summary>View feedback</summary>
  <div>
  
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

## Discussion Modules

### ℹ️ Module 7 Has a Long Name {#module-7 .info}

<details>
  <summary>View feedback</summary>
  <div>
  
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

## References Modules

### ℹ️ Module 8 Has an Even Longer Name {#module-8 .info}

<details>
  <summary>View feedback</summary>
  <div>
  
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>
