---
title: MetaCheck Report
subtitle: "%s"
metacheck:
  version: "%s"
  report-created: "%s"
format:
  html:
    theme: flatly
    toc: true
    toc-location: right
    page-layout: full
    title-block-banner: true
    link-external-newwindow: true
    embed-resources: true
    format-links: false
  pdf: 
    toc: false
---

<style>
  .na::before     { content: '丘쀮잺 '; }
  .fail::before   { content: '丘勇 '; }
  .info::before   { content: '游댯 '; }
  .red::before    { content: '游댮 '; }
  .yellow::before { content: '游리 '; }
  .green::before  { content: '游릭 '; }
  section::before { content: '' !important; }
  .quarto-title-banner { background-color: #327118; }
  th { color: #327118; }
  .dataTables_scrollBody { margin: 0.5em 0; }
</style>

:::: {.content-visible when-format="html"}
::: {.column-margin}
[MetaCheck](http://www.scienceverse.org/metacheck) version {{< meta metacheck.version >}}<br>
Report Created: {{< meta metacheck.report-created >}}  
%s

-------

游릭 no problems detected;  
游리 something to check;  
游댮 possible problems detected;  
游댯 informational only;  
丘쀮잺 not applicable;  
丘勇 check failed
:::
::::

## Demo

Everything below here is for test purposes and removed when using this template to create a report.

## Module A

### Scroll Tables

```{r}
#| echo: false
# table options

cd <- list(list(targets = 4, width = "500px"))
options <- list(dom="t", ordering=FALSE, autoWidth=TRUE,  
                scrollY=200, columnDefs=cd)

# display table
DT::datatable(iris, options, selection = "none", rownames = FALSE)
```


### Collapsible Sections

`r metacheck::collapse_section("Lorem ipsum...")`

## Module B

### Short Tables

A shorter non-scrolling table

```{r}
#| echo: false
# table options
options <- list(dom = "t", ordering = FALSE)

# display table
DT::datatable(head(iris, 2), options, 
              selection = "none", rownames = FALSE)
```

### Wide Scroll Tables

```{r}
#| echo: false
#| column: page
# table options
options <- list(dom = "t", ordering = FALSE , scrollY = 200)

# display table
DT::datatable(mtcars, options, selection = "none", rownames = FALSE)
```

