---
title: MetaCheck Report
subtitle: "To Err is Human: An Empirical Investigation"
metacheck:
  version: "0.0.0.9063"
  report-created: "2025-12-22"
format:
  html:
    theme: 
      light: flatly
      dark: darkly
    respect-user-color-scheme: true
    toc: true
    toc-title: >
      <ul>
        <li class="green">no problems detected;</li>  
        <li class="yellow">something to check;</li> 
        <li class="red">possible problems detected;</li>  
        <li class="info">informational only;</li>  
        <li class="na">not applicable;</li>  
        <li class="fail">check failed</li>
      <ul>
      <hr/>
      **Table of Contents**
    toc-location: right
    toc-expand: 3
    page-layout: full
    title-block-banner: "#327118"
    title-block-banner-color: "white"
    link-external-newwindow: true
    embed-resources: true
    format-links: false
execute: 
  echo: false
  error: true
---

<style>
  main h2, main h3 { margin-left: -20px; }
  main h3 { font-size: 125%; }
  main h4 { font-size: 110%; }
  .na::before     { content: '⚪️ '; }
  .fail::before   { content: '⚫️ '; }
  .info::before   { content: '🔵 '; }
  .red::before    { content: '🔴 '; }
  .yellow::before { content: '🟡 '; }
  .green::before  { content: '🟢 '; }
  section::before { content: '' !important; }
  th { background-color: #555; color: white; }
  table.dataTable, .dataTables_scrollBody { margin: 0.5em 0; }
  #info { position: absolute; top: 2.5em; right: 2.5em; color: white; }
  #info a { color: white !important; }
  .quarto-dark tr.even { background-color: #333; }
  .quarto-dark tr.odd { background-color: #222; }
  .quarto-dark div.datatables { color: white; }
  .quarto-dark table.dataTable { border: 1px solid #555; }
</style>

::: {#info}
[MetaCheck](http://www.scienceverse.org/metacheck) version {{< meta metacheck.version >}}  
Report Created: {{< meta metacheck.report-created >}}  
 <!-- doi, if exists -->
:::


## Summary

- [Preregistration Check](#preregistration-check){.info}: We found 2 preregistrations.  
- [Power](#power){.yellow}: You included power analysis, but did not use an LLM to assess completeness, so should check manually.  
- [Code Check](#code-check){.info}: Some files loaded in the R scripts were missing in the repository. Hardcoded file paths were found. Libraries were loaded in multiple places. Some code files had no comments. No README file was found.   
- [StatCheck](#statcheck){.red}: 1 possible error in t-tests or F-tests  
- [Exact P-Values](#exact-p-values){.red}: We found 1 imprecise *p* value out of 3 detected.  
- [Non-Significant P Value Check](#non-significant-p-value-check){.yellow}: We found 2 non-significant p values that should be checked for appropriate interpretation.  
- [Effect Sizes in t-tests and F-tests](#effect-sizes-in-t-tests-and-f-tests){.red}: We found 1 t-test and/or F-test where effect sizes are not reported.  
- [Marginal Significance](#marginal-significance){.red}: You described 2 effects with terms related to 'marginally significant'.  
- [DOI Check](#doi-check){.yellow}: We checked 1 reference in CrossRef and found 1 missing DOI  
- [Replication Check](#replication-check){.info}: You cited 1 article in the FReD replication database.  
- [RetractionWatch](#retractionwatch){.info}: You cited 1 article in the RetractionWatch database.  
- [Check PubPeer Comments](#check-pubpeer-comments){.info}: You cited 1 reference with comments in PubPeer.  



## Method Modules

### Preregistration Check {.info}

We found 2 preregistrations.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(id = c("<a href='https://osf.io/48ncu' target='_blank'>48ncu</a>", 
"<a href='https://aspredicted.org/by8i8v.pdf' target='_blank'>by8i8v</a>"
), title = c("Papercheck Test", "To err is human"), template = c("OSF Preregistration", 
"AsPredicted")), class = "data.frame", row.names = c(NA, -2L))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

Meta-scientific research has shown that deviations from preregistrations are often not reported or checked, and that the most common deviations concern the sample size. We recommend manually checking the full preregistration at the links below, and have provided the preregistered sample size.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(id = c("48ncu", "by8i8v"), sample_size = c("We randomly assigned 50 scientists to a condition where their manuscript was automatically checked for errors, and 50 scientists to a control condition with a checklist.", 
"We randomly assigned 50 scientists to a condition where their manuscript was automatically checked for errors, and 50 scientists to a control condition with a checklist."
)), row.names = c(NA, -2L), class = c("tbl_df", "tbl", "data.frame"
))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

::: {.callout-tip title="Full Preregistration" collapse="true"}

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(Field = c("template_name", "title", "id", "link", 
"date_created", "date_modified", "date_registered", "embargo_end_date", 
"ia_url", "description", "study_type", "blinding", "study_design_overview", 
"data_collection_started", "existing_data_explanation", "data_collection_procedures", 
"sample_size", "sample_size_rationale", "stopping_rule", "design_independent_variables", 
"design_dependent_variables", "indices", "statistical_tests", 
"inference_criteria", "data_exclusion_criteria", "outliers_and_exclusions", 
"exploratory_analyses", "additional_comments", "research_questions"
), "Preregistration 1" = c("OSF Preregistration", "Papercheck Test", 
"48ncu", "https://osf.io/48ncu", "2025-11-28T19:14:24.639665", 
"2025-08-05T11:55:35.267689", "2025-11-28T19:14:24.608826", "NA", 
"https://archive.org/details/osf-registrations-48ncu-v1", "Automation can be used to check for errors in scientific manuscripts, and inform authors about possible corrections. In this study we examine the usefulness of metacheck to improve best practices.", 
"Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments. This is also known as an intervention experiment and includes randomized controlled trials.", 
"No blinding is involved in this study. ", "Two conditions. In one, researchers receive automated feedback. In the control condition, they do not receive feedback.", 
"Registration prior to creation of data", "", "We will include all scientists who are willing to participate. ", 
"We randomly assigned 50 scientists to a condition where their manuscript was automatically checked for errors, and 50 scientists to a control condition with a checklist.", 
"Based on an a-priori power analysis for an independent t-test, with an expected effect size of d = 0.6, an alpha of 0.05, and a desired power of 0.85, we needed to collect at least 50 participants per group. ", 
"We will stop after data from 100 researchers has been collected.", 
"Two conditions. In one, researchers receive automated feedback. In the control condition, they do not receive feedback.", 
"We will code all manuscripts for mistakes, and count the total number of mistakes per manuscript.", 
"", "We will perform an independent t-test on the number of mistakes in each group.", 
"We will interpret effects as significant if p &lt; .05", "No exclusions are expected.", 
"No missing data is expected.\n", "We also measured the expertise of researchers (in years) to explore whether the automated tool would be more useful, the less research experience researchers had. We also asked researchers to rate how useful they found the checklist or app on a scale from 1 (not at all) to 7 (extremely useful).", 
"", NA), "Preregistration 2" = c("AsPredicted", "To err is human", 
"by8i8v", "https://aspredicted.org/by8i8v.pdf", "2025/11/27 23:20 (PT)", 
NA, NA, NA, NA, NA, NA, NA, "Two conditions. In one, researchers receive automated feedback. In the control condition, they do not receive feedback.", 
NA, "No, no data have been collected for this study yet.", NA, 
"We randomly assigned 50 scientists to a condition where their manuscript was automatically checked for errors, and 50 scientists to a control condition with a checklist.", 
NA, NA, NA, "We will code all manuscripts for mistakes, and count the total number of mistakes per manuscript.", 
NA, "We will perform an independent t-test on the number of mistakes in each group.", 
NA, NA, "none are expected.", NA, "We also measured the expertise of researchers (in years) to explore whether the automated tool would be more useful, the less research experience researchers had. We also asked researchers to rate how useful they found the checklist or app on a scale from 1 (not at all) to 7 (extremely useful).", 
"Automation can be used to check for errors in scientific manuscripts, and inform authors about possible corrections. In this study we examine the usefulness of metacheck to improve best practices."
)), class = "data.frame", row.names = c("template_name", "title", 
"id", "link", "date_created", "date_modified", "date_registered", 
"embargo_end_date", "ia_url", "description", "study_type", "blinding", 
"study_design_overview", "data_collection_started", "existing_data_explanation", 
"data_collection_procedures", "sample_size", "sample_size_rationale", 
"stopping_rule", "design_independent_variables", "design_dependent_variables", 
"indices", "statistical_tests", "inference_criteria", "data_exclusion_criteria", 
"outliers_and_exclusions", "exploratory_analyses", "additional_comments", 
"research_questions"))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "<'top' p>", ordering = FALSE, pageLength = 5, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

:::

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating the rate of deviationsfrom preregistrations, see:

van den Akker O, Bakker M, van Assen M, Pennington C, Verweij L, Elsherif M, Claesen A, Gaillard S, Yeung S, Frankenberger J, Krautter K, Cockcroft J, Kreuer K, Evans T, Heppel F, Schoch S, Korbmacher M, Yamada Y, Albayrak-Aydemir N, Wicherts J (2024). &ldquo;The potential of preregistration in psychology: Assessing preregistration producibility and preregistration-study consistency.&rdquo; <em>Psychological Methods</em>. <a href="https://doi.org/10.1037/met0000687">doi:10.1037/met0000687</a>.

For educational material on how to report deviations from preregistrations, see:

Lakens, Daniël (2024). &ldquo;When and How to Deviate From a Preregistration.&rdquo; <em>Collabra: Psychology</em>, <b>10</b>(1), 117094. <a href="https://doi.org/10.1525/collabra.117094">doi:10.1525/collabra.117094</a>.

:::

### Power {.yellow}

You included power analysis, but did not use an LLM to assess completeness, so should check manually.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("We conducted a sensitivity power analysis to determine that a Cohen's d of 0.50 is the smallest effect size that we could detect with 50 participants in each group and 80% power."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 1, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

Power analyses need to contain the following information to be interpretable: the statistical test, sample size, critical alpha criterion, power level, effect size, and an effect size metric. For example:

> An a priori power analysis for an independent samples t-test, conducted using the pwr.t.test function from pwr (Champely, 2020) with Cohen's d = 0.5 and a critical alpha of p = 0.05, determined that 64 participants are required in each group for 80% power.

## Results Modules

### Code Check {.info}

Below, we describe some best coding practices and give the results of automatic evaluation of these practices in the R files below. This check may miss things or produce false positives if your R scripts are less typical.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("R File Name" = c("bad.R", "bad.Rmd", "analysis.R"
), Download = c("<a href='https://osf.io/download/6935bc117049c887a125cb25/'>download</a>", 
"<a href='https://osf.io/download/uq347/'>download</a>", "<a href='https://raw.githubusercontent.com/Lakens/to_err_is_human/main/analysis.R'>download</a>"
)), row.names = c(NA, -3L), class = c("tbl_df", "tbl", "data.frame"
))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 5, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

#### Missing Files

The scripts load files, but 3 scripts loaded files that could not be automatically identified in the repository. Check if the following files are made available, so that others can reproduce your code, or that the files are missing:

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("R File names" = c("bad.R", "bad.Rmd", "analysis.R"
), "Files loaded in R file but missing in repository" = c("example.csv", 
"example.csv", "file.csv")), row.names = c(NA, -3L), class = c("tbl_df", 
"tbl", "data.frame"))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 5, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

#### Hardcoded Paths

Best programming practice is to use relative file paths instead of hardcoded file paths (e.g., C://Lakens/files) as these folder names are do not exist on other computers. The following hardcoded file paths were found in 3 R file(s).

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("R File names" = c("bad.R", "bad.Rmd", "analysis.R"
), "Absolute paths found" = c("data <- read_csv(\"C://Lakens/files/example.csv\")", 
"data <- read_csv(\"C://Lakens/files/example.csv\"), data2 <- read_csv(\"C://Lakens/files/example2.csv\")", 
"data_1 <- read.csv(\"C:/path/to/a/file.csv\")")), row.names = c(NA, 
-3L), class = c("tbl_df", "tbl", "data.frame"))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 5, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

#### Libraries

Best programming practice is to load all required libraries at one place in the code. In 3 R files, libraries were at multiple places in the R files (i.e., with more than 3 lines in between). This was true in the following R files, where libraries were loaded on the following lines:

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("R File names" = c("bad.R", "bad.Rmd", "analysis.R"
), "Lines at which libraries are loaded" = c("1, 16", "9, 38", 
"1, 16")), row.names = c(NA, -3L), class = c("tbl_df", "tbl", 
"data.frame"))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 5, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

#### Code Comments

Best programming practice is to add comments to code, to explain what the code does (to yourself in the future, or peers who want to re-use your code. The following 1 files had no comments:

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("R File names" = c("bad.R", "bad.Rmd", "analysis.R"
), "Percentage of lines that are comments" = c(0.0526315789473684, 
0.0222222222222222, 0)), row.names = c(NA, -3L), class = c("tbl_df", 
"tbl", "data.frame"))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 5, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

#### README

No README file was found. README files are a way to document the contents and structure of a folder, helping users locate the information they need. You can use a README to document changes to a repository, and explain how files are named. Please consider adding a README.

### StatCheck {.red}

We detected possible errors in test statistics. Note that as the accuracy of statcheck has only been validated for *t*-tests and *F*-tests. As Metacheck only uses validated modules, we only provide statcheck results for *t* tests and *F*-tests.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(Text = "t(97.2) = -1.96, p = 0.152", "Recomputed p" = 0.05286, 
    Section = "results", Sentence = "On average researchers in the experimental condition found the app marginally significantly more useful (M = 5.06) than researchers in the control condition found the checklist (M = 4.5), t(97.2) = -1.96, p = 0.152."), row.names = 2L, class = c("statcheck", 
"data.frame"))

# table setup -----------------------------------
cd <- list(list(targets = 0, width = "10em"))
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific research on the validity of statcheck, and it's usefulness to prevent statistical reporting errors, see:

Nuijten M, van Assen M, Hartgerink C, Epskamp S, Wicherts J (2017). &ldquo;The validity of the tool &quot;statcheck&quot; in discovering statistical reporting inconsistencies.&rdquo; <a href="https://doi.org/10.31234/osf.io/tcxaja">doi:10.31234/osf.io/tcxaja</a>, Preprint.

Nuijten M, Wicherts J (2023). &ldquo;The effectiveness of implementing statcheck in the peer review process to avoid statistical reporting errors.&rdquo; <a href="https://doi.org/10.31234/osf.io/bxau9">doi:10.31234/osf.io/bxau9</a>, Preprint.

:::

### Exact P-Values {.red}

We found 1 imprecise *p* value out of 3 detected. Reporting *p* values imprecisely (e.g., *p* < .05) reduces transparency, reproducibility, and re-use (e.g., in *p* value meta-analyses). Best practice is to report exact p-values with three decimal places (e.g., *p* = .032) unless *p* values are smaller than 0.001, in which case you can use *p* < .001.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("P-Value" = "p > .05", Sentence = "There was no effect of experience on the reduction in errors when using the tool (p > .05), as the correlation was non-significant."), row.names = c(NA, 
-1L), class = c("tbl_df", "tbl", "data.frame"))

# table setup -----------------------------------
cd <- list(list(targets = 0, width = "10%"), list(targets = 1, width = "90%"))
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

The APA manual states: Report exact *p* values (e.g., *p* = .031) to two or three decimal places. However, report *p* values less than .001 as *p* < .001. However, 2 decimals is too imprecise for many use-cases (e.g., a *p* value meta-analysis), so report *p* values with three digits.

American Psychological Association (2020). <em>Publication manual of the American Psychological Association</em>, 7 edition. American Psychological Association.

:::

### Non-Significant P Value Check {.yellow}

We found 2 non-significant p values that should be checked for appropriate interpretation.

Meta-scientific research has shown nonsignificant p values are commonly misinterpreted. It is incorrect to infer that there is 'no effect', 'no difference', or that groups are 'the same' after p > 0.05.

It is possible that there is a true non-zero effect, but that the study did not detect it. Make sure your inference acknowledges that it is possible that there is a non-zero effect. It is correct to include the effect is 'not significantly' different, although this just restates that p > 0.05.

Metacheck does not yet analyze automatically whether sentences which include non-significant p-values are correct, but we recommend manually checking the sentences below for possible misinterpreted non-significant p values.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(Text = c("p = 0.152", "p > .05"), Sentence = c("On average researchers in the experimental condition found the app marginally significantly more useful (M = 5.06) than researchers in the control condition found the checklist (M = 4.5), t(97.2) = -1.96, p = 0.152.", 
"There was no effect of experience on the reduction in errors when using the tool (p > .05), as the correlation was non-significant."
)), row.names = c(NA, -2L), class = c("tbl_df", "tbl", "data.frame"
))

# table setup -----------------------------------
cd <- list(list(targets = 0, width = "10%"), list(targets = 1, width = "90%"))
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating the rate of misinterpretations of non-significant results is high, see:

Aczel B, Palfi B, Szollosi A, Kovacs M, Szaszi B, Szecsi P, Zrubka M, Gronau Q, van den Bergh D, Wagenmakers E (2018). &ldquo;Quantifying Support for the Null Hypothesis in Psychology: An Empirical Investigation.&rdquo; <em>Advances in Methods and Practices in Psychological Science</em>, <b>1</b>(3), 357&ndash;366. <a href="https://doi.org/10.1177/2515245918773742">doi:10.1177/2515245918773742</a>.

Murphy S, Merz R, Reimann L, Fernández A (2025). &ldquo;Nonsignificance misinterpreted as an effect’s absence in psychology: Prevalence and temporal analyses.&rdquo; <em>Royal Society Open Science</em>, <b>12</b>(3), 242167. <a href="https://doi.org/10.1098/rsos.242167">doi:10.1098/rsos.242167</a>.

For educational material on preventing the misinterpretation of p values, see [Improving Your Statistical Inferences](https://lakens.github.io/statistical_inferences/01-pvalue.html#sec-misconception1).

:::

### Effect Sizes in t-tests and F-tests {.red}

We found 1 t-test and/or F-test where effect sizes are not reported. We recommend checking the sentences below, and add any missing effect sizes.

The following sentences are missing effect sizes

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("On average researchers in the experimental condition found the app marginally significantly more useful (M = 5.06) than researchers in the control condition found the checklist (M = 4.5), t(97.2) = -1.96, p = 0.152."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating that effect sizes are often not reported:

* Peng, C.-Y. J., Chen, L.-T., Chiang, H.-M., & Chiang, Y.-C. (2013). The Impact of APA and AERA Guidelines on Effect Size Reporting. Educational Psychology Review, 25(2), 157–209. doi:[10.1007/s10648-013-9218-2](https://doi.org/10.1007/s10648-013-9218-2).

For educational material on reporting effect sizes:

* [Guide to Effect Sizes and Confidence Intervals](https://matthewbjane.quarto.pub/guide-to-effect-sizes-and-confidence-intervals/)

:::

::: {.callout-tip title="All detected and assessed stats" collapse="true"}

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(Sentence = c("On average researchers in the experimental (app) condition made fewer mistakes (M = 9.12) than researchers in the control (checklist) condition (M = 10.9), t(97.7) = 2.9, p = 0.005, d = 0.59.", 
"On average researchers in the experimental condition found the app marginally significantly more useful (M = 5.06) than researchers in the control condition found the checklist (M = 4.5), t(97.2) = -1.96, p = 0.152."
), Section = c("method", "results"), "Effect Size" = c("d = 0.59", 
NA), "Reported Test" = c("t(97.7) = 2.9", "t(97.2) = -1.96"), 
    "Test Type" = c("t-test", "t-test")), row.names = c(NA, -2L
), class = c("tbl_df", "tbl", "data.frame"))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

:::

### Marginal Significance {.red}

You described effects with terms related to 'marginally significant'. If *p* values above 0.05 are interpreted as an effect, you inflate the alpha level, and increase the Type 1 error rate. If a *p* value is higher than the prespecified alpha level, it should be interpreted as a non-significant result.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(section = c("abstract", "results"), text = c("The paper shows examples of (1) open and closed OSF links; (2a) citation of retracted papers, (2b) citations without a doi, (2c) citations with Pubpeer comments, (2d) citations in the FORTT replication database, and (2e) missing/mismatched/incorrect citations and references; (3a) R files with code on GitHub that do not load libraries in one location, (3b) load files that are not shared in the repository, (3c) lack comments, and (3d) have hard-coded files, (4) imprecise reporting of non-significant pvalues; (5) tests with and without effect sizes, (6) use of \"marginally significant\" to describe non-significant findings, and (7) retrieving information from preregistrations.", 
"On average researchers in the experimental condition found the app marginally significantly more useful (M = 5.06) than researchers in the control condition found the checklist (M = 4.5), t(97.2) = -1.96, p = 0.152."
)), row.names = c(NA, -2L), class = c("tbl_df", "tbl", "data.frame"
))

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating the rate at which non-significant p-values are interpreted as marginally significant, see:

Olsson-Collentine, A., van Assen, M. MAL, Hartgerink &amp;, J. CH (2019). &ldquo;The Prevalence of Marginally Significant Results in Psychology Over Time.&rdquo; <em>Psychological Science</em>, <b>30</b>, 576&ndash;586. <a href="https://doi.org/10.1177/0956797619830326">doi:10.1177/0956797619830326</a>.

For the list of terms used to identifify marginally significant results, see this [blog post by Matthew Hankins](https://web.archive.org/web/20251001114321/https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/).

:::

## Reference Modules

### DOI Check {.yellow}

We checked 1 reference in CrossRef and found 1 missing DOI

Double check any references listed in the tables below. The match score gives an indication of how good the match was. Many books do not have a DOI or are not listed in CrossRef. Garbled references are usually a result of poor parsing of the paper by grobid; we are working on more accurate alternatives.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list("Found DOI" = "<a href='https://doi.org/10.1177/2515245918770963' target='_blank'>doi.org/10.1177/2515245918770963</a>", 
    "Match Score" = 79, "Original Reference" = "Lakens D (2018). &ldquo;Equivalence testing for psychological research.&rdquo; <em>Advances in Methods and Practices in Psychological Science</em>, <b>1</b>, 259-270."), row.names = 1L, class = "data.frame")

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

### Replication Check {.info}

We checked 4 references with DOIs. You cited 1 article in the FReD replication database.

Check if you are aware of the replication studies, and cite them where appropriate.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(Reference = "Gangestad SW, Thornhill R (1998). &ldquo;Menstrual cycle variation in women's preferences for the scent of symmetrical men.&rdquo; <em>Proceedings Biological Sciences</em>, <b>22</b>, 927-933. <a href=\"https://doi.org/10.1098/rspb.1998.0380\">doi:10.1098/rspb.1998.0380</a>.", 
    "Replication Reference" = "Jones, B. C., Hahn, A. C., Fisher, C. I., Wang, H., Kandrik, M., Han, C., Fasolt, V., Morrison, D., Lee, A. J., Holzleitner, I. J., O’Shea, K. J., Roberts, S. C., Little, A. C., & DeBruine, L. M. (2018). No Compelling Evidence that Preferences for Facial Masculinity Track Changes in Women’s Hormonal Status. Psychological Science, 29(6), 996-1005. https://doi.org/10.1177/0956797618760197 <a href='https://doi.org/10.1177/0956797618760197' target='_blank'>doi.org/10.1177/0956797618760197</a>"), row.names = c(NA, 
-1L), class = "data.frame")

# table setup -----------------------------------
cd <- list(list(targets = 0, width = "50%"), list(targets = 1, width = "50%"))
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

### RetractionWatch {.info}

We checked 4 references with DOIs. You cited 1 article in the RetractionWatch database.

Check if you are aware of the replication studies, and cite them where appropriate.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(Reference = "Gino F, Wiltermuth SS (2014). &ldquo;Evil Genius? How Dishonesty Can Lead to Greater Creativity.&rdquo; <em>Psychological Science</em>, <b>25</b>(4), 973-981. <a href=\"https://doi.org/10.1177/0956797614520714\">doi:10.1177/0956797614520714</a>.", 
    "RW Type" = "Retraction"), row.names = c(NA, -1L), class = "data.frame")

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

### Check PubPeer Comments {.info}

We checked 4 references with DOIs. You cited 1 reference with comments in PubPeer.

Pubpeer is a platform for post-publication peer review. We have filtered out Pubpeer comments by 'Statcheck'. You can check out the comments by visiting the URLs below:

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(Reference = "Gino F, Wiltermuth SS (2014). &ldquo;Evil Genius? How Dishonesty Can Lead to Greater Creativity.&rdquo; <em>Psychological Science</em>, <b>25</b>(4), 973-981. <a href=\"https://doi.org/10.1177/0956797614520714\">doi:10.1177/0956797614520714</a>.", 
    Comments = 3, "PubPeer Link" = "<a href='https://pubpeer.com/publications/3FA648ECECB88454C91804F09E2E56' target='_blank'>link</a>"), row.names = 1L, class = "data.frame")

# table setup -----------------------------------
cd <- list()
options <- list(dom = "t", ordering = FALSE, pageLength = 2, columnDefs = cd)
DT::datatable(table, options, selection = "none", rownames = FALSE, escape = FALSE)
```

